Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

par(mfrow = c(1, 5))
hist(norm_data[[1]], main = "Sebaran Normal\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#eae1f8")
hist(norm_data[[2]], main = "Sebaran Normal\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#d5bbf3")
hist(norm_data[[3]], main = "Sebaran Normal\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#9d48c7")
hist(norm_data[[4]], main = "Sebaran Normal\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
hist(norm_data[[5]], main = "Sebaran Normal\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#48185b")
```

>>>>

par(mfrow = c(1, 5))
hist(norm_data[[1]], main = "Sebaran Normal\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#e3f4f1")
hist(norm_data[[2]], main = "Sebaran Normal\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#a9ded7")
hist(norm_data[[3]], main = "Sebaran Normal\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#6ec1c1")
hist(norm_data[[4]], main = "Sebaran Normal\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#357a87")
hist(norm_data[[5]], main = "Sebaran Normal\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#0f2c3a")
```
